Survival Analysis

### 2014-05-08 paper.Rnw
More fixing things
Make tests as figures with captions.

\usepackage[margin=1in]{geometry}
\usepackage{nicefrac}
\usepackage{tabularx}
\usepackage{graphicx}

@@

\[ H_0: \S_{ys \leq 12} = \S_{ys > 12} \]
\[ H_a: \S_{ys \leq 12} \neq \S_{ys > 12} \]

@@

\[ H_0: \Lambda_{p = 1} = \Lambda_{p = 0} \]
\[ H_a: \Lambda_{p = 1} \neq \Lambda_{p = 0} \]

\scriptsize
<<bfeed-poverty-test, echo = FALSE>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed)
survdiff(Surv(duration, delta) ~ poverty, data = bfeed.short)
survdiff(Surv(duration, delta) ~ poverty, data = bfeed.tail)
@
\normalsize

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{nicefrac}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}

@@

\[ H_0: S_{ys \leq 12} = S_{ys > 12} \]
\[ H_a: S_{ys \leq 12} \neq S_{ys > 12} \]

@@

\[ H_0: S_{p = 1} = S_{p = 0} \]
\[ H_a: S_{p = 1} \neq S_{p = 0} \]

\begin{figure}[h]
\scriptsize
<<bfeed-poverty-test-normal, echo = FALSE>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed)
@
\normalsize
\label{fig:bfeed-poverty-test-normal}
\caption{Testing $H_0: S_{p = 1} = S_{p = 0}$ for all data}
\end{figure}

\begin{figure}[h]
\scriptsize
<<bfeed-poverty-test-short, echo = FALSE>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed.short)
@
\normalsize
\normalsize
\label{fig:bfeed-poverty-test-short}
\caption{Testing $H_0: S_{p = 1} = S_{p = 0}$ for data truncated at 36 weeks ($d \leq 36$)}
\end{figure}

\begin{figure}[h]
\scriptsize
<<bfeed-poverty-test-tail, echo = FALSE>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed.tail)
@
\normalsize
\normalsize
\label{fig:bfeed-poverty-test-tail}
\caption{Testing $H_0: S_{p = 1} = S_{p = 0}$ for data truncated at 20 weeks ($d \geq 20$)}
\end{figure}
